\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-07-10 paper.tex
Update on Overleaf.
Added Tony as coauthor + updated affiliations

\author{S\'everin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher Wallbridge$^{1}$, Aur\'elie Clodic$^{2}$ and Rachid Alami$^{2}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk},
	$^{2}$Authors are with LAAS-CNRS, Université de Toulouse, CNRS, Toulouse, France
        {\tt\small firstname.surname@laas.fr}}%
}

@@

We are currently deploying a similar network in the framework of the European
project MuMMER where a Pepper robot handles interactive situations in a large
shopping centre in Finland. One of the situation is a guiding task where Pepper
help people to find their route by pointing them landmarks and explaining them
how to reach a destination. To be effevtive, this helping behaviour needs to be
aware of the visual perspective of the human. \uwds facilitates the
implementation of such a spatio-temporal reasoning pipeline, where perception
and high-level reasoning (including complex, human-aware reasoning) have to be
tightly integrated. Because of the decoupling of each of the clients in the
network, \uwds also practically supports software development spread across
multiple partners in different countries, with different expertise.

>>>>

\author{S\'everin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher
Wallbridge$^{3}$,\\
Aur\'elie Clodic$^{2}$, Tony Belpaeme$^{3}$, and Rachid Alami$^{2}$%
\thanks{$^{1}$Author is with Bristol Robotics Lab, University of the West of
England, Bristol, United Kingdom
        {\tt\small severin.lemaignan@brl.ac.uk},
       $^{2}$Authors are with LAAS-CNRS, Universit\'e de Toulouse, CNRS, Toulouse, France
        {\tt\small firstname.surname@laas.fr},
       $^{3}$Authors are with CRNS, Plymouth University, Plymouth, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk}}%
}

@@

We are currently deploying a similar network in the framework of the European
project MuMMER where a Pepper robot handles interactive situations in a large
shopping centre in Finland. One of the situation is a guiding task where Pepper
help people to find their route by pointing them landmarks and explaining them
how to reach a destination. To be effective, this helping behaviour needs to be
aware of the visual perspective of the human. \uwds facilitates the
implementation of such a spatio-temporal reasoning pipeline, where perception
and high-level reasoning (including complex, human-aware reasoning) have to be
tightly integrated. Because of the decoupling of each of the clients in the
network, \uwds also practically supports software development spread across
multiple partners in different countries, with different expertise.
